Reproduce anaylses of Beninca et al (2008)

### 2016-03-23 code/report.Rmd
Improved specification of required R packages

@@

All required libraries:
```{r, message=FALSE}
#install.packages(c("tidyr","dplyr", "lubridate", "stringr",
#                   "ggplot2", "RCurl", "pracma", "oce",
#                   "tseriesChaos", "reshape2", "mgcv", "repmis",
#                   "magrittr", "knitr"))
library(tidyr)
library(dplyr)
library(lubridate)
library(stringr)
library(ggplot2)
library(RCurl)
library(pracma)
library(oce)
library(tseriesChaos)
library(reshape2)
library(mgcv)
library(repmis)
library(magrittr)
library(knitr)
```

>>>>

# R package requirements

The following packages must be installed.

```{r}
#install.packages(c("tidyr","dplyr", "lubridate", "stringr",
#                   "ggplot2", "RCurl", "pracma", "oce",
#                   "tseriesChaos", "reshape2", "mgcv", "repmis",
#                   "magrittr", "knitr", "devtools"))
```

@@

Load required packages:
```{r, message=FALSE}
library(tidyr)
library(dplyr)
library(lubridate)
library(stringr)
library(ggplot2)
library(RCurl)
library(pracma)
library(oce)
library(tseriesChaos)
library(reshape2)
library(mgcv)
library(repmis)
library(magrittr)
library(knitr)
```
